Approaching causal linkages between SES structures and outcomes of the Yellow River Basin, China

### 2022-11-06 docs/papers/01_manuscript/manuscript.tex
docs: E&S submission
BREAKING CHANGE:

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
     Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes are still weaknesses.
     To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
     Under different surface water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role.
     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
     }  %! Notice input

@@

>>>>

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to the depletion of freshwater globally and calls for efficient institutions in water governance. Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes still needs to be improved. To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins. Under different surface water allocation institutions, its streamflow was first overdrawn, dried up, and successfully restored. We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures. We conduct counterfactual identification on the effect of these institutional shifts; our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use. Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role. This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
     }  %! Notice input

@@

% Authors Contribution
% SW and BF designed this research. SS performed the study and analysed data. SS and HW wrote the paper. XW, GC, and HW revised and polished the manuscript and gave significant advice.

% Acknowledgments
% This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities
